---
title: "Assignment - 3 - 37010"
author: "Melanie Tran"
date: "10/30/2020"
output:
  word_document: default
  html_document: default
---

Do Lecture 3 Exercises Q1 to Q3 i.e. factorial, palindrome, and prime number.


1) The factorial of a natural number n is defined as n!=n×(n−1)×(n−2)×⋯×1. Moreover, we define 0!=1. Write an R program that takes a non-negative integer n and computes its factorial n!. Do not use any R’s built-in function such as factorial().
```{r}

#pos numbers 
n <- 5
x <- c(1:n)
answer <- 1

if (n == 0) { 
  answer <- 1
  } else {
    for (i in x) {
      answer <- answer * i
  }
}
answer

```
2) A palindrome is a sequence of characters which reads the same forward or backward. For example, the word “radar”. Write an R program that takes a string and checks if it is a palindrome. Do not make any copy of the sequence of characters. Do not attempt to reverse the sequence of characters. Do not use any R’s built-in function such as rev(), all(), or any(). (Hint: Use strsplit(s, "")[[1]] to split a string into a vector of characters.)

```{r}
s <- "radar"
#test: s <- "Eva, Can I Stab Bats In A Cave?"
#test: s <- "melanie!!"
#test:s <- "hi ih hi ihx"

clean_string <- tolower(gsub(" ", "", gsub("[^[:alnum:] ]", "", s)))

split_string <- strsplit(clean_string, "")[[1]]
original_string <- paste(c(split_string), collapse = "")


#initialize
i <- length(split_string)
reversed_string <- c()

#reverse the string
while (i > 0) { 
  letter <- split_string[i]
  reversed_string <- append(reversed_string,letter)
  i <- i - 1
}

#check if palindrome
if ((paste(c(reversed_string), collapse = "")) == original_string) { 
  print("THIS IS A PALINDROME!")
  } else { 
  print("This is not a palindrome.")
}

```
3) A prime number is a natural number greater than 1 that is not divisible by other numbers except for 1 and itself. Write an R program that takes a natural number n and checks if it is a prime number. Do not use any R’s built-in function such as all() or any(). (Hint: Check if n is divisible by any of 2,…,n−1. Actually, is it necessary to check all of them?)
```{r}

n <- 1249
i <- 999

while (i > 1) { 
  if (n %% i == 0 && i != n) {
    is.prime <- FALSE
    break
  } else { 
      i <- i - 1
      is.prime <- TRUE
  }
}
is.prime

if (is.prime == TRUE) { 
  cat(n, "is a prime number.")
  } else { 
  cat(n, "is NOT a prime number.")
}

```


